Temporal trends (NAMCS)

### 2017-07-27 ms1/namcs_trends.Rmd
FD codes for namcs

sex_codes = read_tsv('../sex-difference/namcs_sex_codes.tsv') %>%
  rename(dx=code)

dx = read_tsv_years('../../db/namcs/data/namcs_dx_%i.tsv') %>%
  left_join(sex_codes, by='dx')

dx_visit = dx %>%
  group_by(visit_id) %>%
  summarize(acute_rc='acute_rc' %in% diagnosis_type)

@@

abx_visit = top_abx %>%
  select(desc, abx) %>%
  left_join(drugs, by='desc') %>%
  count(visit_id, abx) %>% ungroup() %>%
  spread(abx, n)

visits = read_tsv_years('../../db/namcs/data/namcs_visits_%i.tsv') %>%
  mutate(age_group=case_when(.$age <= 19 ~ 'child',
                             .$age <= 64 ~ 'adult',
                             .$age <= 92 ~ 'elderly')) %>%
  left_join(dx_visit, by='visit_id') %>%
  replace_na(list(acute_rc=FALSE)) %>%
  left_join(n_abx, by='visit_id') %>% replace_na(list(n_abx=0)) %>%
  left_join(abx_visit, by='visit_id') %>%
  mutate_at(top_abx$abx, function(x) if_else(is.na(x), 0L, x))
```

@@

>>>>

dx_categories = read_tsv('../../data/fd_codes.tsv') %>%
  mutate(dx=str_pad(code, 5, 'right', '-')) %>%
  select(dx, diagnosis_type)
unique_dx_categories = unique(dx_categories$diagnosis_type)

dx = read_tsv_years('../../db/namcs/data/namcs_dx_%i.tsv') %>%
  left_join(dx_categories, by='dx')

dx_visit = dx %>%
  filter(!is.na(diagnosis_type)) %>%
  mutate(dummy=TRUE) %>%
  select(visit_id, diagnosis_type, dummy) %>%
  distinct() %>%
  spread(diagnosis_type, dummy) %>%
  mutate_if(is.logical, function(x) if_else(is.na(x), FALSE, x))

@@

abx_visit = top_abx %>%
  select(desc, abx) %>%
  left_join(drugs, by='desc') %>%
  count(visit_id, abx) %>% ungroup() %>%
  #mutate(present=n>0) %>% select(-n) %>%
  #spread(abx, present) %>%
  #mutate_if(is.logical, function(x) if_else(is.na(x), FALSE, x))
  spread(abx, n) %>%
  mutate_at(vars(-visit_id), function(x) if_else(is.na(x), 0L, x))

visits = read_tsv_years('../../db/namcs/data/namcs_visits_%i.tsv') %>%
  mutate(age_group=case_when(.$age <= 19 ~ 'child',
                             .$age <= 64 ~ 'adult',
                             .$age <= 92 ~ 'elderly')) %>%
  left_join(dx_visit, by='visit_id') %>%
  left_join(n_abx, by='visit_id') %>% replace_na(list(n_abx=0)) %>%
  left_join(abx_visit, by='visit_id') #%>%
  #mutate_at(top_abx$abx, function(x) if_else(is.na(x), 0L, x))
```

@@

## Diagnoses

### Levofloxacin

The NAMCS data can actually confirm that, not only is levo going up per visit, it's going up faster in those with URIs (and not for pneumonia). (Here I'm looking at the entire population.)

```{r levo_dx}
svyglm(levo ~ year*uri + year*pneumonia, design=design, family='poisson') %>%
  tidy %>%
  kable
```

### Cephalexin

We can also confirm that keflex is going up because of UTIs and now because of SSTIs (even though the use of keflex for UTIs is so much smaller than for SSTIs):

```{r keflex_dx}
svyglm(keflex ~ year*ssti + year*uti, design=design, family='poisson') %>%
  tidy %>%
  kable
```
